\documentclass{article}
\usepackage{scimisc-cv}


\title{Zijian Xu CV}
\author{Zijian Xu}
\date{July 2020}

\cvname{Zijian Xu}
\cvpersonalinfo{
Tel: 412-618-6098 \cvinfosep
Email: zix10@pitt.edu \cvinfosep
Linkedln: https://www.linkedin.com/in/zijianxu-sde/
}

\begin{document}

\makecvtitle 

\section{EDUCATION}
\begin{itemize}
\item \cvsubsection{University of Pittsburgh}[Pittsburgh, Pennsylvania]
[MS, Information Science][Aug 2019 to Present]

\item \cvsubsection{Nanjing University of Posts and Telecommunication}[Nanjing, China]
[BS, Electrical Engineering][Aug 2015 to Jul 2019]
\end{itemize}
 
\section{Technical Skills}

\begin{itemize}
\item 
\textbf{Programming Language:}
\textbf{\textit{\underline{Java (proficient)}}}, 
JavaScript (prior experience)
\item 
\textbf{Software Development:} 
SQL (
MySQL, 
\textbf{\textit{\underline{PostgreSQL}}}), 
NoSQL (
\textbf{\textit{\underline{DynomaDB}}},  \textbf{\textit{\underline{MongoDB}}}, 
Neo4j), 
git, 
\textbf{\textit{\underline{AWS}}}, 
Docker
\item 
\textbf{Libraries and Frameworks:} 
\textbf{\textit{\underline{Spring MVC (proficient)}}}, 
\textbf{\textit{\underline{Angular (prior experience)}}}, 
React, 
Node.js(Express, Nest), 
Ionic


\end{itemize}
 
\section{Working Experience}

\cvsubsection{Amazon}[Seattle, Washington]
[Software Development Engineer Intern][Jun 2020 to Present]

\begin{itemize}
 \item[] \textit{Implemented an \textbf{\textit{\underline{email automation system}}}. Reduced hundreds of agents' workload and \textbf{\textit{\underline{increased team efficiency by 20\%}}} by using Java, DynamoDB, S3, SES, Spring framework, React Library. }
 
 \item Created a new thread for \textbf{\textit{\underline{scheduled task}}} with \textbf{\textit{\underline{Spring}}}. The automation can only run at a specific time \textbf{\textit{\underline{with offsets}}}. Emails can only be sent to customers worldwide at working time.
 
 \item Created new tables with \textbf{\textit{\underline{DynamoDB}}}. Making sure that customer information was not stored in table, keep the security of the system.
 
 \item Made external calls with account id to decrepit customer information.
 
 \item Stored emails' html-templates in \textbf{\textit{\underline{S3}}}. Called Apis to get templates based on different situations. Emails can provide different options and advice for different customers.
 
 \item Set \textbf{\textit{\underline{SES}}} sand box mode and sent emails with SES server. Tracked emails sending status. Customers can receive emails and make further steps based on sending status.
 
 \item Worte \textbf{\textit{\underline{unit test}}} with \textbf{\textit{\underline{Junit}}} and \textbf{\textit{\underline{Mockito}}}. Making sure that each method I added will get the result I wanted. The whole system will not be merged into branch before unit testing. The codes in branch is all in a good quality.
 
 \item Designed a visualization table for agents with \textbf{\textit{\underline{React}}}. Stored actions with \textbf{\textit{\underline{Redux}}}. Agents can easily track the automation process and make actions with those customers' email cannot be sent.
\end{itemize}


\cvsubsection{University of Pittsburgh School of Health and Rehabilitation Sciences}[Pittsburgh, Pennsylvania][Full Stack Developer][Dec 2019 to Present]
\begin{itemize}
\item Develop \textbf{\textit{\underline{mobile apps}}} and \textbf{\textit{\underline{portals}}} for clinicians. Helped patients take part in different \textbf{\textit{\underline{medical projects}}} with easier way. Helped doctors get messages of different cases on time. Using Spring framework, Angular framework, Express.js and Ionic framework.

\item Designed \textbf{\textit{\underline{Geo-navigation system mock up}}} for disabled person for both outdoor and indoor purpose. Helped people in wheelchair get safest and shortest way. Helped people find education sources nearby.

\item Develop \textbf{\textit{\underline{directories website}}} with \textbf{\textit{\underline{WordPress}}} and  Google Map API. Provided family caregivers information about different origination as well as their locations and website. \textbf{\textit{\underline{Saved 30\% of time}}} for caregivers.
\end{itemize}

\cvsubsection{FanoLabs}[Shenzheng, China][Software Testing Engineer][Feb 2019 to May 2019]
\begin{itemize}
\item Wrote  \textbf{\textit{\underline{Cypress scripts}}} for web automation testing. The automation can mock thousands of people click one button at the same time. Making \textbf{\textit{\underline{pressure test}}} easier and make sure website will not have problems in high peak period before being deployed.

\item Called APIs and got http responses. Visualized different status code in the website with \textbf{\textit{\underline{React}}}. The other developers can easily figure out how many failures will be in one day.
\end{itemize}


 
\section{Project Experience}

\cvsubsection{Clockwork}[University of Pittsburgh School of Health and Rehabilitation Sciences]
[Responsibility: Implement backend][Feb 2020 to Present]

\begin{itemize}
\item Created \textbf{\textit{\underline{RESTFUL API}}} with \textbf{\textit{\underline{Spring MVC}}}. Created a new \textbf{\textit{\underline{annotation}}} for web filter. When calling apis, annotation will help me filter those ids are not a patient id.

\item Implemented \textbf{\textit{\underline{Web Socket}}} in Spring. When patients registering accounts or reporting activities, clinicians can receive notifications on time. Clinicians will not miss any activities. 

\item Deployed \textbf{\textit{\underline{PostgreSQL}}} to \textbf{\textit{\underline{AWS RDS}}} for testing purpose. All teammates with different Dev-computers can test with the same data.
\end{itemize}

\cvsubsection{ltgo}[University of Pittsburgh School of Health and Rehabilitation Sciences]
[Responsibility: Implement both backend and frontend][Feb 2020 to Present]
\begin{itemize}
\item Created RESTFUL API with \textbf{\textit{\underline{Express.js}}}. Applied \textbf{\textit{\underline{JWT}}} for autorization. Four different Roles will be distinguished by token. 

\item Created a bar chart with \textbf{\textit{\underline{Angular}}}. Visualized patients' every day steps for clinicians. Helped doctors save 20\% of time.
\end{itemize}

\section{Other Skills}
\begin{description}[widest=Languages]
\item[Languages]	English (professional proficiency), Mandarin (native) 
\end{description}


\end{document}
